\section{Assignment Assessment}
\subsection{Kenneth}
I think that the assignment was a good introduction to running a service that should stay operational over a short time period. I think that the course should have done this as an lab exercise. This would greatly improve the communication and collaboration between students and groups in this course. Besides that I would like to say that this is one of the more interesting courses I’ve taken so far. I’m beginning to get the feeling that we are using our expertise in order to make something useful on a somewhat larger scale than previous courses. This inspires me to work rather than thinking of the course as homework. To the students next year I would advise them to make more use of group meetings rather than work separate, both outside and inside the team.
\subsection{Kent}
I think the assignment was really interesting and fun to work with. Don’t know if I would change anything in particular. It could maybe been introduced a little better about the SLA’s and how we were supposed to meet/change this. How we could check if it was met etc. I remember from the implementation presentation that a lot of the questions regarding the system was related to whether or not they met the SLA. And since we hadn’t had any operating time yet, or knew how we could check whether or not we met the SLA, it was hard to give a good answer. 

All in all it was a good experience to get some insight in how to set up a server and other things connected to that. It’s probably not that relevant to the education, but it was a valuable experience. 
\subsection{Kristy}
Doing this project has improved my knowledge in system management as well as increasing my interest in this topic. 
I like do it because it has been a good experience working on a big project like this as we have to talk with other groups which are involved in the task. 
\subsection{Jose}
This assignment is a really good introduction to understand how to coordinate the work with separate teams and how to manage a computer system. I would not change it so much. For example, more activity during operation period could have been better. Anyway, since there are much more courses and all of us have more work to do, I see really nice the workload this project requires.
